The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-06-01 brains-introduction.tex
feat/introduction: first try at a new introduction

>>>>

\todo{
\#14: Rework to
(1) present shifts in biology (eco-evo-devo) rejoining attempts to bridge social/cognitive rift and study knowledge transmission (cultural evolution),
(2) present current problem of testing theories to incorporate those discoveries,
(3) introduce the question of cultural attractors,
(4) present big data literature which can bring measurement tools,
(5) to be studied through quotes on the web: it's the proposal of an online approach, we'll be describing and cross-checking with existing literature (vs. predicting, since there are too many possible things to predict)
}

\todo{\#20: check text/flow/definitions for clarity against Gureckis' edited pdf}

\begin{new}
Since the very beginning of psychology, of social sciences, and later that of cognitive science, several authors have proposed frameworks to unify the study of cognition and culture in meaningful ways.
In social science, the question already existed in Durkheim's initial works \CN, but was only later tackled in earnest by Mauss' \emph{Techniques of the Body} \CN, Giddens' \emph{Structuration Theory} \CN and Bourdieu's \emph{Sens Pratique} \CN.

Today's debate of that question, however, is structured by proponents from cognitive science.
There is, on one side, a theory allying neo-darwinism and representation-based cognitive science that is best summarized by Sperber in his description of \emph{Epidemiology of Representations} \CN, complementary to Boyd and Richerson's work on gene-culture co-evolution \CN.
On the other side an enactive proposition which anthropologists like Ingold, in line with Mauss' works, are calling for \CN, is being developed by Froese, Di Paolo, and De Jaegher among others \CNs.

The question is also gaining relevance in other fields, as work in evo-devo and non-genetic inheritance is accumulating evidence not accounted for by the modern synthesis \CN;
these discoveries are creating demand for new or extended approaches to life evolution that unify its different levels, as well as creative empirical methods to test the predictions these approaches make \CN.

\end{new}
